Generalization Errors of Hard Parameter Sharing: High-dimensional Asymptotics and Implications

### 2020-09-26 arxiv/proof_gaussian_case.tex
wip

%\input{proof_two_tasks}
The main goal of this section is to prove Theorem \ref{thm_main_RMT}.
%Recall that $n:=n_1+n_2$, which is the total number of data in the two tasks.
%Before giving the main proof, we first introduce some notations and tools.
%Following the notations in \cite{EKYY,EKYY1}, we will use the following definition to characterize events of overwhelming probability.
%
%\begin{definition}[overwhelming probability event] \label{high_prob}
%Define
%\begin{equation}\label{def_phi}
%\varphi:=(\log N)^{\log \log N}.
%\end{equation}
%We say that an $N$-dependent event $\Omega$ holds with {\it{$\xi$-overwhelming probability}} if there exist constant $c,C>0$ independent of $N$, such that
%\begin{equation}
%\mathbb{P}(\Omega) \geq 1-N^{C} \exp(- c\varphi^{\xi}),  \label{D25}
%\end{equation}
%for all sufficiently large $N$. For simplicity, for the case $\xi=1$, we just say {\it{overwhelming probability}}. Note that if (\ref{D25}) holds, then $\mathbb P(\Omega) \ge 1 - \exp(-c'\varphi^{\xi})$ for any constant $0\le c' <c$.
%\end{definition}
%\begin{remark}
%For any $c, C>0$, there exists a $0< c^{\prime}<c$, such that $N^{C} \exp(-c \varphi^{\xi}) \leq \exp(-c^{\prime} \varphi^{\xi})$. Hence, if
%\begin{equation}
%\mathbb{P}(\Omega) \geq 1- \exp(-c \varphi^{\xi})
%\end{equation}
%$\Omega$ is also a $\xi$-overwhelming probability event.
%\end{remark}
For simplicity of notations, we will use the following notion of stochastic domination, which was first introduced in \cite{Average_fluc} and subsequently used in many works on random matrix theory. It greatly simplifies the presentation of the results and their proofs by systematizing statements of the form ``$\xi$ is bounded by $\zeta$ with overwhelming probability up to a small power of $n$".

\begin{definition}[Stochastic domination]\label{stoch_domination}
%\begin{itemize}
%\item[(i)]
Let $\xi\equiv \xi^{(n)}$ and $\zeta\equiv \zeta^{(n)}$ be two $n$-dependent random variables.
%\begin{itemize} \item[(i)]
We say $\xi$ is stochastically dominated by $\zeta$, denoted by $\xi\prec \zeta$ or $\xi=\OO_\prec(\zeta)$, if for any (small) constant $\e>0$ and (large) constant $D>0$,
\[ \bbP\left(|\xi| >n^\e |\zeta|\right)\le n^{-D}\]
for large enough $n\ge n_0(\e, D)$. Moreover, if $\xi$ and $\zeta$ depend on a parameter $u$, then we say $\xi$ is stochastically dominated by $\zeta$ uniformly in $u\in \cal U$,  if for any constants $\e,D>0$,
\[\sup_{u\in \cal U}\bbP\left(|\xi(u)|>n^\e |\zeta(u)|\right)\le n^{-D}\]
for large enough $n\ge n_0(\e, D)$.
%\item[(ii)]
%\end{itemize}
%(i) Let
%\[\xi=\left(\xi^{(n)}(u):n\in\bbN, u\in U^{(n)}\right),\hskip 10pt \zeta=\left(\zeta^{(n)}(u):n\in\bbN, u\in U^{(n)}\right)\]
%be two families of nonnegative random variables, where $U^{(n)}$ is a possibly $n$-dependent parameter set. We say $\xi$ is stochastically dominated by $\zeta$, uniformly in $u$, if for any fixed (small) $\epsilon>0$ and (large) $D>0$,
%\[\sup_{u\in U^{(n)}}\bbP\left[\xi^{(n)}(u)>n^\epsilon\zeta^{(n)}(u)\right]\le n^{-D}\]
%for large enough $n\ge n_0(\epsilon, D)$, and we shall use the notation $\xi\prec\zeta$.
%%Throughout this paper, the stochastic domination will always be uniform in all parameters that are not explicitly fixed (such as matrix indices, and $z$ that takes values in some compact set).
%%Note that $N_0(\epsilon, D)$ may depend on quantities that are explicitly constant, such as $\tau$ in Assumption \ref{assm_big1} and equation \eqref{assm_gap}.
%If for some complex family $\xi$ we have $|\xi|\prec\zeta$, then we will also write $\xi \prec \zeta$ or $\xi=\OO_\prec(\zeta)$.
%\item[(ii)]
%(ii) We extend the definition of $\OO_\prec(\cdot)$ to matrices in the weak operator sense as follows. Let $A$ be a family of random matrices and $\zeta$ be a family of nonnegative random variables. Then $A=O_\prec(\zeta)$ means that $\left|\left\langle\mathbf v, A\mathbf w\right\rangle\right|\prec\zeta \| \mathbf v\|_2 \|\mathbf w\|_2 $ uniformly in any deterministic vectors $\mathbf v$ and $\mathbf w$. Here and throughout the following, whenever we say ``uniformly in any deterministic vectors", we mean that ``uniformly in any deterministic vectors belonging to a set of cardinality $N^{\OO(1)}$".
%\item[(iv)]
%\end{itemize}
\end{definition}
\begin{remark}
Note that since we allow an $n^\e$ factor in the definition of stochastic domination, we have the seemingly strange inequality $(\log n)^C\prec 1$ for any constant $C>0$.
\end{remark}

\begin{example}\label{example stoc}
Given a random variable $\xi$, if its moments exist up to any order, then we have $|\xi|\prec 1$. In fact, for any constants $\e, D>0$, by Markov's inequality we have
$$ \P(|\xi|\ge n^{\e})\le n^{-k\e}{\E |\xi|^k}\le n^{-D},$$
if we choose $k$ large enough such that $k\e>D$. As a special case, we have $|\xi|\prec 1$ for a Gaussian random variable $\xi$ with unit variance.
\end{example}

%\HZ{Why is this below part of the def. of stochastic domination?}
In the following proof, we say an event $\Xi$ holds with overwhelming probability if for any constant $D>0$, $\mathbb P(\Xi)\ge 1- n^{-D}$ for large enough $n$. Moreover, we say $\Xi$ holds with overwhelming probability in an event $\Omega$ if for any constant $D>0$, $\mathbb P(\Omega\setminus \Xi)\le n^{-D}$ for large enough $n$.

@@

\begin{remark}
The lower bound $\rho_2\ge 1+\tau$ in equation \eqref{assm2} is to ensure that the sample covariance matrix $(X^{(2)})^\top X^{(2)}$ is non-singular with overwhelming probability. Moreover, we have allowed that $\rho_1=0$, because we want to state a general result that also covers the special case with no source task.
\end{remark}

\begin{remark}\label{rem_athmoment}
Whenever the estimates in equation \eqref{eq_support} hold, we say $n^{-1/2}Z^{(1)}$ and $n^{-1/2}Z^{(2)}$ satisfy the {\it{bounded support condition}} with $q$, or $n^{-1/2}Z^{(1)}$ and $n^{-1/2}Z^{(2)}$ have support $q$.
%\begin{definition}\label{defn_support}
%We say a (rescaled) random matrix $\cal M$ satisfies the {\it{bounded support condition}} with $q$, if
%\begin{equation}
%\max_{i,j}\vert \cal M_{ij}\vert \prec q. \label{eq_support}
%\end{equation}
%%Here $q\equiv q(n)$ is a deterministic parameter and usually satisfies $ n^{-{1}/{2}} \leq q \leq n^{- \phi} $ for some (small) constant $\phi>0$.
%Whenever (\ref{eq_support}) holds, we say that $M$ has support $q$.
%%Moreover, if the entries of $X$ satisfy (\ref{size_condition}), then $X$ trivially satisfies the bounded support condition with $q=N^{-\phi}$.
%\end{definition}
%\begin{example}
%\todo{Talk about the Gaussian case and Bernoulli case.}
By Example \ref{example stoc}, if the entries of $Z^{(1)}$ have finite moments up to any order, %as in equation \eqref{assmAhigh},
then $n^{-1/2}Z^{(1)}$ has bounded support $n^{-1/2}$. More generally, if the entries of $Z^{(1)}$ have finite $\varphi$-th moment as in \eqref{assmAhigh}, then using Markov's inequality and a simple union bound we get that
\be\label{Ptrunc}
\P\left(n^{-1/2}\max_{i,\mu}|(Z^{(1)})_{\mu i}|\ge (\log n) n^{-\frac{\varphi-4}{2\varphi}}\right)=\OO((\log n)^{-\varphi}).\ee
In other words, $n^{-1/2}Z^{(1)}$ has bounded support $q=n^{-\frac{\varphi-4}{2\varphi}}$ on a event with probability $1-\oo(1)$. This leads to the exponent $\frac{\varphi-4}{2\varphi}$ in Fact \ref{lem_minv}. %This fact will be used in the proof of Corollary \ref{main_cor} below.
The above discussion shows that the bounded support condition provides great flexibility in dealing with finite moment conditions.
%is essentially introduced to deal with the moment conditions; see Corollary \ref{main_cor} below for more details.
%\end{example}
\end{remark}

\paragraph{Notations.}
Define the index sets
$$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
 We will consistently use the latin letters $i,j\in\sI_{0}$ and greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$. Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
 \be\label{labelZ}
 Z^{(1)}= (Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1), \quad Z^{(2)}= (Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2).\ee

\subsection{Warmup: The Gaussian Case}
Now we give a heuristic derivation of the matrix limit when the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d. Gaussian. In this case,
%However, notice that if the entries of $(Z^{(1)})\equiv (Z^{(1)})^{\text{Gauss}}$ and $(Z^{(2)})\equiv (Z^{(2)})^{\text{Gauss}}$ are i.i.d. Gaussian, then
by the rotational invariance of the multivariate Gaussian distribution we have
\be\label{eq in Gauss} Z^{(1)} U\Lambda \stackrel{d}{=} Z^{(1)} \Lambda, \quad Z^{(2)} V \stackrel{d}{=} Z^{(2)},\ee
where ``$\stackrel{d}{=}$" means ``equal in distribution". Hence it suffices to consider the following resolvent
 \begin{equation} \label{resolv Gauss1}
   G(z)= \left( {\begin{array}{*{20}c}
   { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
   {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
   {n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
   \end{array}} \right)^{-1}.
 \end{equation}

\medskip
\noindent\textbf{Deriving the self-consistent equations.} Now taking average of equation \eqref{1self_Gmu}, we obtain that
\be\label{2self_Gmu} m_1= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad m_2=\frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},
\ee
with overwhelming probability. As a byproduct, comparing equations \eqref{1self_Gmu} and \eqref{2self_Gmu}, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
\be\label{2.5self_Gmu} G_{\mu \mu }=m_1 +\oo(1),\quad G_{\nu\nu}=m_2+\oo(1),\ee
with overwhelming probability. Together with the definition of $m$ and $m_0$ in equation \eqref{defm}, the two equations in equation \eqref{2self_Gmu} give that
\be\label{3self_Gmu}  \frac1{m_1}= -1- \frac{1}{n} \sum_{i=1}^p \lambda_i^2 G_{ii}+ \oo(1),\quad \frac1{m_2}=-1-\frac{1}{n} \sum_{i=1}^p G_{ii}  + \oo(1),\ee
with overwhelming probability. Plugging equation \eqref{1self_Gii} into equation \eqref{3self_Gmu}, we obtain that
\be\label{approximate m1m2}
\begin{split}
& \frac1{m_1}= -1+ \frac{1}{n} \sum_{i=1}^p \frac{\lambda_i^2 }{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}+ \oo(1),\\
& \frac1{m_2}=-1+\frac{1}{n} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}  + \oo(1),
\end{split}
\ee
with overwhelming probability, which give a system of approximate self-consistent equations for $(m_1,m_2)$.
A rigorous derivation of these two equations will be given in the proof of Lemma \ref{lemm_selfcons_weak}. Compare \eqref{approximate m1m2} to the deterministic self-consistent equations in equation \eqref{selfomega_a}, one can observe that we should have
\be\label{approx m12 add}
(m_1,m_2) =\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)+\oo(1) \quad \text{with overwhelming probability. }
\ee
To justify this identity rigorously, we need to know that the self-consistent equations are stable, that is, a small perturbation of the equations leads to a small perturbation of the solution. This will be given by Lemma \ref{lem_stabw}.

\medskip
\noindent\textbf{Deriving the matrix limit.}  Inserting the approximate identity \eqref{approx m12 add} into equations \eqref{1self_Gii} and \eqref{2.5self_Gmu}, we get that for  $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
$$G_{ii}(z)=(-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1)^{-1},\quad G_{\mu\mu}=-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z)+\oo(1),\quad G_{\nu\nu}=-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)+\oo(1),$$
with overwhelming probability. These explain the diagonal entries of $\Gi$ in equation \eqref{defn_piw}. For the off-diagonal entries, they are close to zero due to concentration. For example, for $i\ne j\in \cal I_1$, by Schur complement formula in equation (\ref{resolvent3}), we have
$$G_{ij}=-G_{ii}\Big({\lambda_i}{n^{-1/2}}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j} + {n^{-1/2}}\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j} \Big).$$
Using Lemma \ref{largedeviation}, we can show that $n^{-1/2}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j}$ and $n^{-1/2}\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j}$ are both close to zero. The other off-diagonal entries can be bounded in the same way. The bound on the off-diagonal entries will be proved rigorously in Lemma \ref{Z_lemma}.

>>>>

The main goal of this section is to prove Theorem \ref{thm_main_RMT}.
We begin by providing a warm up analysis when the entries of $Z^{(1)}$ and $Z^{(2)}$ are drawn i.i.d. from an isotropic Gaussian distribution.
%However, notice that if the entries of $(Z^{(1)})\equiv (Z^{(1)})^{\text{Gauss}}$ and $(Z^{(2)})\equiv (Z^{(2)})^{\text{Gauss}}$ are i.i.d. Gaussian, then
By the rotational invariance of the multivariate Gaussian distribution, we have
\be\label{eq in Gauss} Z^{(1)} U\Lambda \stackrel{d}{=} Z^{(1)} \Lambda, \quad Z^{(2)} V \stackrel{d}{=} Z^{(2)},\ee
where ``$\stackrel{d}{=}$" means ``equal in distribution". Hence it suffices to consider the following resolvent
 \begin{equation} \label{resolv Gauss1}
   G(z)= \left( {\begin{array}{*{20}c}
   { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
   {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
   {n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
   \end{array}} \right)^{-1}.
 \end{equation}
Define the index sets
$$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
 We will consistently use the latin letters $i,j\in\sI_{0}$ and greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$. Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
 \be\label{labelZ}
 Z^{(1)}= (Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1), \quad Z^{(2)}= (Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2).\ee

\medskip
\noindent\textbf{Self-consistent equations.} Now taking average of equation \eqref{1self_Gmu}, we obtain that
\be\label{2self_Gmu} m_1= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad m_2=\frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},
\ee
with overwhelming probability. As a byproduct, comparing equations \eqref{1self_Gmu} and \eqref{2self_Gmu}, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
\be\label{2.5self_Gmu} G_{\mu \mu }=m_1 +\oo(1),\quad G_{\nu\nu}=m_2+\oo(1),\ee
with overwhelming probability. Together with the definition of $m$ and $m_0$ in equation \eqref{defm}, the two equations in equation \eqref{2self_Gmu} give that
\be\label{3self_Gmu}  \frac1{m_1}= -1- \frac{1}{n} \sum_{i=1}^p \lambda_i^2 G_{ii}+ \oo(1),\quad \frac1{m_2}=-1-\frac{1}{n} \sum_{i=1}^p G_{ii}  + \oo(1),\ee
with overwhelming probability. Plugging equation \eqref{1self_Gii} into equation \eqref{3self_Gmu}, we obtain that
\be\label{approximate m1m2}
\begin{split}
& \frac1{m_1}= -1+ \frac{1}{n} \sum_{i=1}^p \frac{\lambda_i^2 }{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}+ \oo(1),\\
& \frac1{m_2}=-1+\frac{1}{n} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}  + \oo(1),
\end{split}
\ee
with overwhelming probability, which give a system of approximate self-consistent equations for $(m_1,m_2)$.
A rigorous derivation of these two equations will be given in the proof of Lemma \ref{lemm_selfcons_weak}. Compare \eqref{approximate m1m2} to the deterministic self-consistent equations in equation \eqref{selfomega_a}, one can observe that we should have
\be\label{approx m12 add}
(m_1,m_2) =\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)+\oo(1) \quad \text{with overwhelming probability. }
\ee
To justify this identity rigorously, we need to know that the self-consistent equations are stable, that is, a small perturbation of the equations leads to a small perturbation of the solution. This will be given by Lemma \ref{lem_stabw}.

\medskip
\noindent\textbf{The matrix limit.}  Inserting the approximate identity \eqref{approx m12 add} into equations \eqref{1self_Gii} and \eqref{2.5self_Gmu}, we get that for  $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
$$G_{ii}(z)=(-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1)^{-1},\quad G_{\mu\mu}=-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z)+\oo(1),\quad G_{\nu\nu}=-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)+\oo(1),$$
with overwhelming probability. These explain the diagonal entries of $\Gi$ in equation \eqref{defn_piw}. For the off-diagonal entries, they are close to zero due to concentration. For example, for $i\ne j\in \cal I_1$, by Schur complement formula in equation (\ref{resolvent3}), we have
$$G_{ij}=-G_{ii}\Big({\lambda_i}{n^{-1/2}}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j} + {n^{-1/2}}\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j} \Big).$$
Using Lemma \ref{largedeviation}, we can show that $n^{-1/2}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j}$ and $n^{-1/2}\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j}$ are both close to zero. The other off-diagonal entries can be bounded in the same way. The bound on the off-diagonal entries will be proved rigorously in Lemma \ref{Z_lemma}.

\paragraph{Notations.}
We say an event $\Xi$ holds with overwhelming probability if for any constant $D>0$, $\mathbb P(\Xi)\ge 1- n^{-D}$ for large enough $n$. Moreover, we say $\Xi$ holds with overwhelming probability in an event $\Omega$ if for any constant $D>0$, $\mathbb P(\Omega\setminus \Xi)\le n^{-D}$ for large enough $n$.
We frequently use the following notion of stochastic domination, which was first introduced in \cite{Average_fluc} and subsequently used in many works on random matrix theory.
%It greatly simplifies the presentation of the results and their proofs by systematizing statements of the form ``$\xi$ is bounded by $\zeta$ with overwhelming probability up to a small power of $n$".

\begin{definition}[Stochastic domination]\label{stoch_domination}
%\begin{itemize}
%\item[(i)]
Let $\xi\equiv \xi^{(n)}$ and $\zeta\equiv \zeta^{(n)}$ be two $n$-dependent random variables.
\HZ{what is $n$-dependent rv?}
We say $\xi$ is stochastically dominated by $\zeta$, denoted by $\xi\prec \zeta$ or $\xi=\OO_\prec(\zeta)$, if for any (small) constant $\e>0$ and (large) constant $D>0$
\[ \bbP\left(|\xi| >n^\e |\zeta|\right)\le n^{-D}, \]
for large enough $n\ge n_0(\e, D)$. Moreover, if $\xi$ and $\zeta$ depend on a parameter $u$, then we say $\xi$ is stochastically dominated by $\zeta$ uniformly in $u\in \cal U$,  if for any constants $\e,D>0$,
\[\sup_{u\in \cal U}\bbP\left(|\xi(u)|>n^\e |\zeta(u)|\right)\le n^{-D}, \]
for large enough $n\ge n_0(\e, D)$.
%\item[(ii)]
%\end{itemize}
%(i) Let
%\[\xi=\left(\xi^{(n)}(u):n\in\bbN, u\in U^{(n)}\right),\hskip 10pt \zeta=\left(\zeta^{(n)}(u):n\in\bbN, u\in U^{(n)}\right)\]
%be two families of nonnegative random variables, where $U^{(n)}$ is a possibly $n$-dependent parameter set. We say $\xi$ is stochastically dominated by $\zeta$, uniformly in $u$, if for any fixed (small) $\epsilon>0$ and (large) $D>0$,
%\[\sup_{u\in U^{(n)}}\bbP\left[\xi^{(n)}(u)>n^\epsilon\zeta^{(n)}(u)\right]\le n^{-D}\]
%for large enough $n\ge n_0(\epsilon, D)$, and we shall use the notation $\xi\prec\zeta$.
%%Throughout this paper, the stochastic domination will always be uniform in all parameters that are not explicitly fixed (such as matrix indices, and $z$ that takes values in some compact set).
%%Note that $N_0(\epsilon, D)$ may depend on quantities that are explicitly constant, such as $\tau$ in Assumption \ref{assm_big1} and equation \eqref{assm_gap}.
%If for some complex family $\xi$ we have $|\xi|\prec\zeta$, then we will also write $\xi \prec \zeta$ or $\xi=\OO_\prec(\zeta)$.
%\item[(ii)]
%(ii) We extend the definition of $\OO_\prec(\cdot)$ to matrices in the weak operator sense as follows. Let $A$ be a family of random matrices and $\zeta$ be a family of nonnegative random variables. Then $A=O_\prec(\zeta)$ means that $\left|\left\langle\mathbf v, A\mathbf w\right\rangle\right|\prec\zeta \| \mathbf v\|_2 \|\mathbf w\|_2 $ uniformly in any deterministic vectors $\mathbf v$ and $\mathbf w$. Here and throughout the following, whenever we say ``uniformly in any deterministic vectors", we mean that ``uniformly in any deterministic vectors belonging to a set of cardinality $N^{\OO(1)}$".
%\item[(iv)]
%\end{itemize}
\end{definition}

For example, we say that $\xi$ is stochastically dominated by $\zeta$ with overwhelming probability if $\zeta$ is greater than $\xi$ up to a small power of $n^{\e}$.
Since we allow an $n^\e$ factor in the definition of stochastic domination, we have the seemingly strange inequality $(\log n)^C\prec 1$ for any constant $C>0$.
As another example, given a random variable $\xi$, if its moments exist up to any order, then we have $|\xi|\prec 1$. In fact, for any constants $\e, D>0$, by Markov's inequality we have
$$ \P(|\xi|\ge n^{\e})\le n^{-k\e}{\E |\xi|^k}\le n^{-D},$$
if we choose $k$ large enough such that $k\e>D$. As a special case, we have $|\xi|\prec 1$ for a Gaussian random variable $\xi$ with unit variance.

%\HZ{Why is this below part of the def. of stochastic domination?}

@@

%\begin{remark}
%The lower bound $\rho_2\ge 1+\tau$ in equation \eqref{assm2} is to ensure that the sample covariance matrix $(X^{(2)})^\top X^{(2)}$ is non-singular with overwhelming probability. Moreover, we have allowed that $\rho_1=0$, because we want to state a general result that also covers the special case with no source task.
%\end{remark}

Whenever the estimates in equation \eqref{eq_support} hold, we say $n^{-1/2}Z^{(1)}$ and $n^{-1/2}Z^{(2)}$ satisfy the {\it{bounded support condition}} with $q$, or $n^{-1/2}Z^{(1)}$ and $n^{-1/2}Z^{(2)}$ have support $q$.
%\begin{definition}\label{defn_support}
%We say a (rescaled) random matrix $\cal M$ satisfies the {\it{bounded support condition}} with $q$, if
%\begin{equation}
%\max_{i,j}\vert \cal M_{ij}\vert \prec q. \label{eq_support}
%\end{equation}
%%Here $q\equiv q(n)$ is a deterministic parameter and usually satisfies $ n^{-{1}/{2}} \leq q \leq n^{- \phi} $ for some (small) constant $\phi>0$.
%Whenever (\ref{eq_support}) holds, we say that $M$ has support $q$.
%%Moreover, if the entries of $X$ satisfy (\ref{size_condition}), then $X$ trivially satisfies the bounded support condition with $q=N^{-\phi}$.
%\end{definition}
%\begin{example}
%\todo{Talk about the Gaussian case and Bernoulli case.}
As shown in the example above, if the entries of $Z^{(1)}$ have finite moments up to any order, %as in equation \eqref{assmAhigh},
then $n^{-1/2}Z^{(1)}$ has bounded support $n^{-1/2}$. More generally, if the entries of $Z^{(1)}$ have finite $\varphi$-th moment as in \eqref{assmAhigh}, then using Markov's inequality and a simple union bound we get that
\be\label{Ptrunc}
\P\left(n^{-1/2}\max_{i,\mu}|(Z^{(1)})_{\mu i}|\ge (\log n) n^{-\frac{\varphi-4}{2\varphi}}\right)=\OO((\log n)^{-\varphi}).\ee
In other words, $n^{-1/2}Z^{(1)}$ has bounded support $q=n^{-\frac{\varphi-4}{2\varphi}}$ on a event with probability $1-\oo(1)$. This leads to the exponent $\frac{\varphi-4}{2\varphi}$ in Fact \ref{lem_minv}. %This fact will be used in the proof of Corollary \ref{main_cor} below.
The above discussion shows that the bounded support condition provides great flexibility in dealing with finite moment conditions.
%\end{example}

%Recall that $n:=n_1+n_2$, which is the total number of data in the two tasks.
%Before giving the main proof, we first introduce some notations and tools.
%Following the notations in \cite{EKYY,EKYY1}, we will use the following definition to characterize events of overwhelming probability.
%
%\begin{definition}[overwhelming probability event] \label{high_prob}
%Define
%\begin{equation}\label{def_phi}
%\varphi:=(\log N)^{\log \log N}.
%\end{equation}
%We say that an $N$-dependent event $\Omega$ holds with {\it{$\xi$-overwhelming probability}} if there exist constant $c,C>0$ independent of $N$, such that
%\begin{equation}
%\mathbb{P}(\Omega) \geq 1-N^{C} \exp(- c\varphi^{\xi}),  \label{D25}
%\end{equation}
%for all sufficiently large $N$. For simplicity, for the case $\xi=1$, we just say {\it{overwhelming probability}}. Note that if (\ref{D25}) holds, then $\mathbb P(\Omega) \ge 1 - \exp(-c'\varphi^{\xi})$ for any constant $0\le c' <c$.
%\end{definition}
%\begin{remark}
%For any $c, C>0$, there exists a $0< c^{\prime}<c$, such that $N^{C} \exp(-c \varphi^{\xi}) \leq \exp(-c^{\prime} \varphi^{\xi})$. Hence, if
%\begin{equation}
%\mathbb{P}(\Omega) \geq 1- \exp(-c \varphi^{\xi})
%\end{equation}
%$\Omega$ is also a $\xi$-overwhelming probability event.
%\end{remark}
